Pretty darn good control: when are approximate solutions better than approximate models

### 2023-01-20 code/plots.Rmd
manuscript figures, plots

@@

```{r}
actions <- unique(msy$action)
i <- which.min(abs(actions - best$action* 0.8))
tac_sim <- msy |> 
  filter(action == actions[[i]]) |>
  pivot_longer(c("X", "Y", "Z"),
               names_to = "species", values_to = "abundance")
tac_sim |>
  filter(rep < 20) |>
  ggplot(aes(t, abundance,  col=species)) + 
    geom_line() + facet_wrap(~rep)

@@

```{r}
ppo_sim
```

@@

```{r}
all_sim |> 
    mutate(across(type, factor, levels = c("Opt const mortality", "80% opt const mortality", 
                                           "DRL"))) |>
    group_by(rep, type) |>
    filter(rep == 0) |>
    ggplot(aes(t, abundance, col = species)) + 
        geom_line()  + 
        facet_wrap(~type) + 
        labs(y = "reward", x = "repetition")
all_sim |>
    group_by(rep,type) |>
    filter(rep<10) |>
    ggplot(aes(t, action)) + 
    geom_line()  + 
    facet_wrap(~type) + 
    labs(y = "action", x = "repetition")

>>>>

```{r}
best_reward(msy)
```

@@

```{r}
actions <- unique(msy$action)

tac_sim <- msy |> 
  filter(action == actions[[i]]) |>
  pivot_longer(c("X", "Y", "Z"),
               names_to = "species", values_to = "abundance")
tac_sim |>
  filter(rep < 20) |>
  ggplot(aes(t, abundance,  col=species)) + 
    geom_line() + facet_wrap(~rep)

@@

```{r}
ppo_sim
ppo_sim |> within(rm("reward"))
ppo_sim
```

@@

```{r}
all_sim |> 
    mutate(across(type, factor, levels = c("Opt const mortality", "80% opt const mortality", 
                                           "DRL"))) |>
    group_by(rep, type) |>
    filter(rep == 0) |>
    ggplot(aes(t, abundance, col = species)) + 
        geom_line()  + 
        facet_wrap(~type) + 
        labs(y = "reward", x = "repetition") +
        theme(aspect.ratio = 2/5)
all_sim |>
    group_by(rep,type) |>
    filter(rep<10) |>
    ggplot(aes(t, action)) + 
    geom_line()  + 
    facet_wrap(~type) + 
    labs(y = "action", x = "repetition")

### 2023-01-20 manuscript/manuscript.Rmd
manuscript figures, plots

# rename some columns for figure purposes:
colnames(msy) <- c('t', 'rep', 'action', 'reward', 'X', 'Y', 'Z')
colnames(ppo) <- c('1', 't', 'X', 'Y', 'Z', 'action', 'reward', 'rep')

@@

i <- which.min(abs(actions - best$action* 0.8))
tac_sim <- msy |> 
    filter(action == actions[[i]]) |>
    pivot_longer(c("X", "Y", "Z"),
        names_to = "species", values_to = "abundance") |>
    mutate(abundance = abundance + 1, policy = "tac")

ppo_sim <- ppo |> 
    mutate(escapement = (X+1) - action * (X+1),
        effort = action) |>
    pivot_longer(c("X", "Y", "Z"),
        names_to = "species", values_to = "abundance") |>
    mutate(policy = "ppo") # already in natural units

best_e <- 0.62 # optimal constant escapement, computed from ../data/escapement.csv.gz
esc_sim <- escapement |> 
    rename(escapement = action) |>
    filter(escapement == best_e) |> # data had a naming problem
    pivot_longer(c("X", "Y", "Z"),
        names_to = "species", values_to = "abundance") |>
    mutate(abundance = abundance + 1)
```

>>>>

# rename some columns for figure purposes:
colnames(msy) <- c('t', 'rep', 'action', 'reward', 'X', 'Y', 'Z')
colnames(ppo) <- c('1', 't', 'X', 'Y', 'Z', 'action', 'reward', 'rep')
colnames(escapement) <- c('t', 'rep', 'action', 'reward', 'X', 'Y', 'Z')

@@

i <- which.min(abs(actions - best_action* 0.8))
tac_sim <- msy |> 
    filter(action == actions[[i]]) |>
    pivot_longer(c("X", "Y", "Z"),
        names_to = "species", values_to = "abundance") |>
    mutate(abundance = abundance + 1, policy = "tac")

ppo_sim <- ppo |> 
    pivot_longer(c("X", "Y", "Z"),
        names_to = "species", values_to = "abundance") |>
    within(rm("1")) |>
    mutate(policy = "ppo") # already in natural units

best_e <- 0.62 # optimal constant escapement, computed from ../data/escapement.csv.gz
esc_sim <- escapement |> 
    rename(escapement = action) |>
    filter(escapement == best_e) |> # data had a naming problem
    pivot_longer(c("X", "Y", "Z"),
        names_to = "species", values_to = "abundance") |>
    mutate(abundance = abundance + 1)

msy_tac_ppo <- bind_rows(msy_sim, tac_sim, ppo_sim)
#head(msy_tac_ppo)
#head(ppo_sim)
```
